Semantic Preserving Bijective Mappings for Expressions involving Special Functions between Computer Algebra Systems and Document Preparation Systems

### 2019-06-27 _arxiv.tex

\documentclass[a4paper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel} 
\usepackage[T1]{fontenc}
\usepackage{hyperref}	
\usepackage[acronym, nomain]{glossaries} 
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{parskip}		
\usepackage{txfonts}			
\usepackage{enumitem}			
\usepackage{algorithm}
\usepackage{algpseudocode} 
\usepackage{lipsum} 
\usepackage{tabularx}
\usepackage{stmaryrd}
\usepackage{float}
\usepackage{csquotes}
\usepackage{layout}
\usepackage{textcomp} 
\usepackage{authblk}
\usepackage{comgipp}

>>>>

\documentclass[a4paper,11pt]{article}
\begin{filecontents*}{references.bib}
	@article{GreinerPetter2019,
		author={Greiner-Petter, Andre and Schubotz, Moritz and Cohl, Howard S. and Gipp, Bela},
		date={2019-07},
		title={Semantic Preserving Bijective Mappings for Expressions involving Special Functions in Computer Algebra Systems and Document Preparation Systems},
		doi={10.1108/AJIM-08-2018-0185},
		number={3}, 
		volume={71},
		issn={2050-3806},
		journal={Aslib Journal of Information Management},
		pages={415--439}, 
	}
\end{filecontents*}
\begin{filecontents*}{./bibliography.bib}
% Encoding: UTF-8

@InProceedings{MCAT,
	author    = {Giovanni Yoko Kristianto and
		Goran Topic and
		Akiko Aizawa},
	title     = {{MCAT} Math Retrieval System for {NTCIR-12} MathIR Task},
	booktitle = {Proceedings of the 12th {NTCIR} Conference on Evaluation of Information
		Access Technologies, National Center of Sciences, Tokyo, Japan, June
		7-10, 2016},
	year      = {2016},
	crossref  = {NTCIR:2016},
	url       = {http://research.nii.ac.jp/ntcir/workshop/OnlineProceedings12/pdf/ntcir/MathIR/04-NTCIR12-MathIR-KristiantoGY.pdf},
	timestamp = {Tue, 07 Feb 2017 18:49:02 +0100},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/ntcir/KristiantoTA16},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@InProceedings{SIGIR:Semantification,
	author    = {Moritz Schubotz and
		Alexey Grigorev and
		Marcus Leich and
		Howard S. Cohl and
		Norman Meuschke and
		Bela Gipp and
		Abdou S. Youssef and
		Volker Markl},
	title     = {Semantification of Identifiers in Mathematics for Better Math Information
		Retrieval},
	booktitle = {Proceedings of the 39th International {ACM} {SIGIR} conference on
		Research and Development in Information Retrieval, {SIGIR} 2016, Pisa,
		Italy, July 17-21, 2016},
	pages     = {135--144},
	year      = {2016},
	crossref  = {SIGIR:2016},
	url       = {http://doi.acm.org/10.1145/2911451.2911503},
	doi       = {10.1145/2911451.2911503},
	timestamp = {Mon, 05 Jun 2017 12:41:48 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/sigir/SchubotzGLCMGYM16},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@InProceedings{CICM:Paper,
	author    = {Howard S. Cohl and
		Moritz Schubotz and
		Abdou Youssef and
		Andr{\'{e}} Greiner{-}Petter and
		J{\"{u}}rgen Gerhard and
		Bonita V. Saunders and
		Marjorie A. McClain and
		Joon Bang and
		Kevin Chen},
	title     = {Semantic Preserving Bijective Mappings of Mathematical Formulae Between
		Document Preparation Systems and Computer Algebra Systems},
	booktitle = {Intelligent Computer Mathematics - 10th International Conference,
		{CICM} 2017, Edinburgh, UK, July 17-21, 2017, Proceedings},
	pages     = {115--131},
	year      = {2017},
	crossref  = {CICM:2017},
	url       = {https://doi.org/10.1007/978-3-319-62075-6_9},
	doi       = {10.1007/978-3-319-62075-6_9},
	timestamp = {Wed, 28 Jun 2017 13:10:13 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/mkm/CohlSYGGSMBC17},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@InProceedings{DRMF:15,
	author    = {Howard S. Cohl and
		Moritz Schubotz and
		Marjorie A. McClain and
		Bonita V. Saunders and
		Cherry Y. Zou and
		Azeem S. Mohammed and
		Alex A. Danoff},
	title     = {Growing the Digital Repository of Mathematical Formulae with Generic \LaTeX{}
		Sources},
	booktitle = {Intelligent Computer Mathematics - International Conference, {CICM}
		2015, Washington, DC, USA, July 13-17, 2015, Proceedings},
	pages     = {280--287},
	year      = {2015},
	crossref  = {CICM:MKM:2015},
	url       = {https://doi.org/10.1007/978-3-319-20615-8_18},
	doi       = {10.1007/978-3-319-20615-8_18},
	timestamp = {Sun, 04 Jun 2017 10:10:26 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/mkm/CohlSMSZMD15},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@InProceedings{DRMF:14,
	author    = {Howard S. Cohl and
		Marjorie A. McClain and
		Bonita V. Saunders and
		Moritz Schubotz and
		Janelle C. Williams},
	title     = {Digital Repository of Mathematical Formulae},
	booktitle = {Intelligent Computer Mathematics - International Conference, {CICM}
		2014, Coimbra, Portugal, July 7-11, 2014. Proceedings},
	pages     = {419--422},
	year      = {2014},
	crossref  = {CICM:MKM:14},
	url       = {https://doi.org/10.1007/978-3-319-08434-3_30},
	doi       = {10.1007/978-3-319-08434-3_30},
	timestamp = {Sun, 04 Jun 2017 10:10:26 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/mkm/CohlMSSW14},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@InProceedings{AISC:MultivaluedFunctions,
	author    = {James H. Davenport},
	title     = {The Challenges of Multivalued "Functions"},
	booktitle = {Intelligent Computer Mathematics, 10th International Conference, {AISC}
		2010, 17th Symposium, Calculemus 2010, and 9th International Conference,
		{MKM} 2010, Paris, France, July 5-10, 2010. Proceedings},
	pages     = {1--12},
	year      = {2010},
	crossref  = {AISC:2010},
	url       = {https://doi.org/10.1007/978-3-642-14128-7_1},
	doi       = {10.1007/978-3-642-14128-7_1},
	timestamp = {Thu, 01 Jun 2017 18:57:42 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/aisc/Davenport10},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@InProceedings{Planetary,
	author    = {Michael Kohlhase and
		Joseph Corneli and
		Catalin David and
		Deyan Ginev and
		Constantin Jucovschi and
		Andrea Kohlhase and
		Christoph Lange and
		Bogdan Matican and
		Stefan Mirea and
		Vyacheslav Zholudev},
	title     = {The Planetary System: Web 3.0 {\&} Active Documents for {STEM}},
	booktitle = {Proceedings of the International Conference on Computational Science,
		{ICCS} 2011, Nanyang Technological University, Singapore, 1-3 June,
		2011},
	pages     = {598--607},
	year      = {2011},
	crossref  = {ICCS:2011},
	url       = {https://doi.org/10.1016/j.procs.2011.04.063},
	doi       = {10.1016/j.procs.2011.04.063},
	timestamp = {Thu, 08 Jun 2017 09:07:49 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/journals/procedia/KohlhaseCDGJKLMMZ11},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@InProceedings{MaxTract,
	author    = {Josef B. Baker and Alan P. Sexton and Volker Sorge},
	title     = {MaxTract: Converting {PDF} to \LaTeX, MathML and Text},
	booktitle = {Intelligent Computer Mathematics - 11th International Conference, {AISC} 2012, 19th Symposium, Calculemus 2012, 5th International Workshop, {DML} 2012, 11th International Conference, {MKM} 2012, Systems and Projects, Held as Part of {CICM} 2012, Bremen, Germany, July 8-13, 2012. Proceedings},
	year      = {2012},
	pages     = {422--426},
	bibsource = {dblp computer science bibliography, http://dblp.org},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/aisc/BakerSS12},
	crossref  = {CICM:2012},
	doi       = {10.1007/978-3-642-31374-5_29},
	timestamp = {Fri, 19 May 2017 01:25:05 +0200},
	url       = {https://doi.org/10.1007/978-3-642-31374-5_29},
}

@InProceedings{JOBAD:orig,
	author    = {Jana Giceva and
		Christoph Lange and
		Florian Rabe},
	title     = {Integrating Web Services into Active Mathematical Documents},
	booktitle = {Intelligent Computer Mathematics, 16th Symposium, Calculemus 2009,
		8th International Conference, {MKM} 2009, Held as Part of {CICM} 2009,
		Grand Bend, Canada, July 6-12, 2009. Proceedings},
	pages     = {279--293},
	year      = {2009},
	crossref  = {CICM:2009},
	url       = {https://doi.org/10.1007/978-3-642-02614-0_24},
	doi       = {10.1007/978-3-642-02614-0_24},
	timestamp = {Thu, 15 Jun 2017 21:43:52 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/mkm/GicevaLR09},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@InProceedings{POM-Tagger,
	author    = {Abdou Youssef},
	title     = {Part-of-Math Tagging and Applications},
	booktitle = {Intelligent Computer Mathematics - 10th International Conference,
		{CICM} 2017, Edinburgh, UK, July 17-21, 2017, Proceedings},
	pages     = {356--374},
	year      = {2017},
	crossref  = {CICM:2017},
	url       = {https://doi.org/10.1007/978-3-319-62075-6_25},
	doi       = {10.1007/978-3-319-62075-6_25},
	timestamp = {Wed, 28 Jun 2017 13:10:13 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/mkm/Youssef17},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@InProceedings{MLP:Project,
	author    = {Robert Pagel and
		Moritz Schubotz},
	title     = {Mathematical Language Processing Project},
	booktitle = {Joint Proceedings of the MathUI, OpenMath and ThEdu Workshops and
		Work in Progress track at {CICM} co-located with Conferences on Intelligent
		Computer Mathematics {(CICM} 2014), Coimbra, Portugal, July 7-11,
		2014.},
	year      = {2014},
	crossref  = {CICM:2014:Workshop},
	url       = {http://ceur-ws.org/Vol-1186/paper-23.pdf},
	timestamp = {Mon, 30 May 2016 16:28:38 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/mkm/PagelS14},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@InProceedings{VMEXT,
	author    = {Moritz Schubotz and
		Norman Meuschke and
		Thomas Hepp and
		Howard S. Cohl and
		Bela Gipp},
	title     = {{VMEXT:} {A} Visualization Tool for Mathematical Expression Trees},
	booktitle = {Intelligent Computer Mathematics - 10th International Conference,
		{CICM} 2017, Edinburgh, UK, July 17-21, 2017, Proceedings},
	pages     = {340--355},
	year      = {2017},
	crossref  = {CICM:2017},
	url       = {https://doi.org/10.1007/978-3-319-62075-6_24},
	doi       = {10.1007/978-3-319-62075-6_24},
	timestamp = {Wed, 28 Jun 2017 13:10:13 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/mkm/SchubotzMHCG17},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@InProceedings{MATLAB,
	author    = {Cleve B. Moler},
	title     = {{MATLAB:} {A} Mathematical Visualization Laboratory},
	booktitle = {COMPCON'88, Digest of Papers, Thirty-Third {IEEE} Computer Society International Conference, San Francisco, California, USA, February 29 - March 4, 1988},
	year      = {1988},
	pages     = {480--481},
	bibsource = {dblp computer science bibliography, http://dblp.org},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/compcon/Moler88a},
	crossref  = {IEEE:88},
	doi       = {10.1109/CMPCON.1988.4915},
	timestamp = {Mon, 29 May 2017 15:06:13 +0200},
	url       = {https://doi.org/10.1109/CMPCON.1988.4915},
}

@InProceedings{NumericalTests:Paper,
	author    = {Cohl, H.~S. and Greiner-Petter, A. and Schubotz, M.},
	title     = {Automated Symbolic and Numerical Testing of {DLMF} Formulae using Computer Algebra Systems},
	booktitle = {Proceedings of the 11th Conference on
		Intelligent Computer Mathematics, {CICM} 2018, RISC, Hagenberg, Austria},
	year      = {2018},
	note		= {Accepted Full Paper}
}

@Book{SF:Book, 
	place={Cambridge}, 
	series={Encyclopedia of Mathematics and its Applications}, 
	title={Special Functions}, 
	DOI={10.1017/CBO9781107325937}, 
	ISBN={9781107325937},
	publisher={Cambridge University Press}, 
	author={Andrews, George E. and Askey, Richard and Roy, Ranjan}, 
	year={1999}, 
	collection={Encyclopedia of Mathematics and its Applications}
}

@Article{CRC,
	author   = {W. W. Peterson and D. T. Brown},
	title    = {{C}yclic {C}odes for {E}rror {D}etection},
	journal  = {Proceedings of the IRE},
	year     = {1961},
	volume   = {49},
	number   = {1},
	pages    = {228--235},
	month    = jan,
	issn     = {0096-8390},
	doi      = {10.1109/JRPROC.1961.287814},
	keywords = {Binary codes;Data communication;Decoding;Encoding;Error correction codes;Feedback;Fires;Information theory;Mathematics;Polynomials},
}

@Book{CF:Handbook,
	author    = {Annie A. M. Cuyt and
		Vigidis Brevik Petersen and
		Brigitte Verdonk and
		Haakon Waadeland and
		William B. Jones},
	title     = {Handbook of Continued Fractions for Special Functions},
	publisher = {Springer},
	year      = {2008},
	url       = {http://www.springer.com/de/book/9781402069482#aboutBook},
	isbn      = {978-1-4020-6948-2},
	timestamp = {Fri, 10 Apr 2015 15:54:50 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/books/daglib/0035147},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@Article{CF:Maple,
	author = {Backeljauw, Franky and Cuyt, Annie},
	title = {Algorithm 895: A Continued Fractions Package for Special Functions},
	journal = {ACM Trans. Math. Softw.},
	issue_date = {July 2009},
	volume = {36},
	number = {3},
	month = jul,
	year = {2009},
	issn = {0098-3500},
	pages = {15:1--15:20},
	articleno = {15},
	numpages = {20},
	url = {http://doi.acm.org/10.1145/1527286.1527289},
	doi = {10.1145/1527286.1527289},
	acmid = {1527289},
	publisher = {ACM},
	address = {New York, NY, USA},
	keywords = {CAS software, Maple, continued fractions, special functions},
}

@Misc{CF:eCF,
	author       = {Michael Trott and Eric Wolfgang Weisstein},
	title        = {Computational Knowledge of Continued Fractions},
	howpublished = {\newline\url{http://blog.wolframalpha.com/2013/05/16/computational-knowledge-of-continued-fractions}},
	month        = may,
	year         = {2013},
	note         = {seen 3/2017},
}

@Article{MCAT:MathSemanticSearch,
	author    = {Shunsuke Ohashi and
		Giovanni Yoko Kristianto and
		Goran Topic and
		Akiko Aizawa},
	title     = {Efficient Algorithm for Math Formula Semantic Search},
	journal   = {{IEICE} Transactions},
	volume    = {99-D},
	number    = {4},
	pages     = {979--988},
	year      = {2016},
	url       = {http://search.ieice.org/bin/summary.php?id=e99-d_4_979},
	timestamp = {Wed, 13 Apr 2016 19:55:11 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/journals/ieicet/OhashiKTA16},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@InProceedings{SymbolDec,
	author = {Wolska, Magdalena and Grigore, Mihai},
	title = {Symbol Declarations in Mathematical Writing},
	booktitle = {Towards a Digital Mathematics Library. Paris, France, July 7-8th,
		2010},
	year = {2010},
	pages = {119--127},
	publisher = {Masaryk University Press},
	abstract = {We present three corpus-based studies on symbol declaration in mathematical
		writing. We focus on simple object denoting symbols which may be
		part of larger expressions. We look into whether the symbols are
		explicitly introduced into the discourse and whether the information
		on once interpreted symbols can be used to interpret structurally
		related symbols. Our goal is to support fine-grained semantic interpretation
		of simple and complex mathematical expressions. The results of our
		analysis empirically show the potential benefit of using larger discourse
		context in automated disambiguation of mathematical expressions.},
	groups = {GuidiReview, phd-m},
	keywords = {mathematical discourse; disambiguation of mathematical expressions;
		corpus-based analysis; mathematical discourse},
	location = {Brno, Czech Republic},
	owner = {Moritz},
	timestamp = {2016.10.05},
	url = {http://eudml.org/doc/221086}
}

@TechReport{eCF:FinalReport,
	author      = {Michael Trott and Eric Weisstein and Oleg Marichev and Todd Rowland},
	title       = {The eCF-Project -- Final Report},
	institution = {Wolfram Foundation},
	year        = {2013},
	month       = {oct},
	timestamp   = {2016-04-24},
	url         = {http://www.wolframfoundation.org/programs/FinalReport.pdf},
}

@Book{OMDoc,
	title     = {OMDoc - An Open Markup Format for Mathematical Documents [version 1.2]},
	publisher = {Springer},
	year      = {2006},
	author    = {Michael Kohlhase},
	series    = {Lecture Notes in Computer Science},
	isbn      = {3-540-37897-9},
	bibsource = {dblp computer science bibliography, http://dblp.org},
	biburl    = {http://dblp.uni-trier.de/rec/bib/books/sp/Kohlhase06},
	doi       = {10.1007/11826095},
	timestamp = {Tue, 16 May 2017 14:01:44 +0200},
	url       = {https://doi.org/10.1007/11826095},
}

@Article{NIST:DLMF:Paper,
	author    = {Daniel W. Lozier},
	title     = {{NIST} Digital Library of Mathematical Functions},
	journal   = {Ann. Math. Artif. Intell.},
	volume    = {38},
	number    = {1-3},
	pages     = {105--119},
	year      = {2003},
	url       = {https://doi.org/10.1023/A:1022915830921},
	doi       = {10.1023/A:1022915830921},
	timestamp = {Sun, 28 May 2017 13:20:59 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/journals/amai/Lozier03},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@online{NIST:DLMF,
	key = "{\relax DLMF}",
	title = "{\relax DLMF}",
	url = "http://dlmf.nist.gov/",
	note = "{\it NIST Digital Library of Mathematical Functions}. Release 1.0.20 of 2018-09-15. F.~W.~J. Olver, A.~B. {Olde Daalhuis}, D.~W. Lozier, B.~I. Schneider,
	R.~F. Boisvert, C.~W. Clark, B.~R. Miller and B.~V. Saunders, editors"
}

@Book{Notation:History,
	title     = {A History of Mathematical Notations},
	publisher = {Dover Publications Inc.},
	year      = {1994},
	author    = {Cajori, Florian},
	isbn      = {0486677664},
	date      = {1994-03-01},
	ean       = {9780486677668},
	pagetotal = {848},
	url       = {http://www.ebook.de/de/product/1683538/florian_cajori_a_history_of_mathematical_notations.html},
}

@Article{Branches:acot,
	author    = {Robert M. Corless and
		David J. Jeffrey and
		Stephen M. Watt and
		James H. Davenport},
	title     = {"According to Abramowitz and Stegun" or arccoth needn't be uncouth},
	journal   = {{ACM} {SIGSAM} Bulletin},
	volume    = {34},
	number    = {2},
	pages     = {58--65},
	year      = {2000},
	url       = {http://doi.acm.org/10.1145/362001.362023},
	doi       = {10.1145/362001.362023},
	timestamp = {Tue, 16 May 2017 14:05:56 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/journals/cca/CorlessJWD00},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@Book{MAPLE:ProgrammingGuide,
	title     = {Maple~2016 Programming Guide},
	publisher = {Maplesoft, a division of Waterloo Maple Inc.},
	year      = {2016},
	author    = {L. Bernardin and P. Chin and P. DeMarco and K. O. Geddes and D. E. G. Hare and K. M. Heal and G. Labahn and J. P. May and J. McCarron and M. B. Monagan and D. Ohashi and S. M. Vorkoetter},
	isbn      = {978-1-926902-46-3},
}

@TechReport{MathML,
	author       = {Ron Ausbrooks and Stephen Buswell and David Carlisle and Giorgi Chavchanidze and St{\'e}phane Dalmas and Stan Devitt and Angel Diaz and Sam Dooley and Roger Hunter and Patrick Ion and Michael Kohlhase and Azzeddine Lazrek and Paul Libbrecht and Bruce Miller and Robert Miner (deceased) and Chris Rowley and Murray Sargent and Bruce Smith and Neil Soiffer and Robert Sutor and Stephen Watt},
	title        = {Mathematical Markup Language (MathML) 3},
	institution  = {International Organization for Standardization (ISO)},
	year         = {2014},
	note         = {Version 3.0 2nd Edition},
	organization = {World Wide Web Consortium (W3C)},
	url          = {https://www.w3.org/TR/MathML3/},
}

@Misc{Wiki,
	author       = {Wikimedia Foundation},
	title        = {Wikipedia},
	howpublished = {\url{https://en.wikipedia.org}},
	month        = {01},
	year         = {2001},
}

@Book{Knuth,
	title     = {The Art of Computer Programming, Volume {I:} Fundamental Algorithms, 3rd Edition},
	publisher = {Addison-Wesley},
	year      = {1997},
	author    = {Donald Ervin Knuth},
	isbn      = {0201896834},
	bibsource = {dblp computer science bibliography, http://dblp.org},
	biburl    = {http://dblp.uni-trier.de/rec/bib/books/lib/Knuth97},
	timestamp = {Wed, 03 May 2017 18:39:06 +0200},
	url       = {http://www.worldcat.org/oclc/312910844},
}

@Misc{Maple:ImportExport,
	author       = {Maplesoft},
	title        = {{Produce output suitable for LaTeX 2e}},
	howpublished = {\url{http://www.maplesoft.com/support/help/Maple/view.aspx?path=latex}},
	note         = {Since version Maple 18, Seen 06/2017},
	skipbib      = {true},
}

@Misc{Mathematica:ImportExport,
	author       = {Wolfram Research},
	title        = {Generating and Importing TeX},
	howpublished = {\url{https://reference.wolfram.com/language/tutorial/GeneratingAndImportingTeX.html}},
}

@Misc{Matlab:ImportExport,
	author       = {MathWorks},
	title        = {\LaTeX{} form of symbolic expression in MATLAB},
	howpublished = {\url{https://www.mathworks.com/help/symbolic/latex.html}},
	note         = {Seen 06/2017},
}

@Misc{Sagetex,
	author       = {Dan Drake},
	title        = {sagetex},
	howpublished = {\url{https://ctan.org/tex-archive/macros/latex/contrib/sagetex/}},
	month        = {06},
	year         = {2009},
	note         = {Seen 06/2017},
	organization = {Comprehensive},
}

@Misc{LatexCalc,
	author       = {Berkeley Churchill and Steven Boyd},
	title        = {\LaTeX{Calc}},
	howpublished = {\url{https://sourceforge.net/projects/latexcalc/}},
	year         = {2010},
	note         = {Seen 06/2017},
}

@InProceedings{MathDox,
	author = { Hans Cuypers and Arjeh M. Cohen and Jan Willem Knopper and Rikko Verrijzer and Mark Spanbroek },
	title = { MathDox, a system for interactive Mathematics },
	editor = { Joseph Luca and Edgar R. Weippl },
	booktitle = { Proceedings of EdMedia: World Conference on Educational Media and Technology 2008 },
	year = { 2008 },
	month = { June },
	pages = { 5177--5182 },
	address = { Vienna, Austria },
	publisher = { Association for the Advancement of Computing in Education (AACE) },
	url = { https://www.learntechlib.org/p/29092 },
	abstract = { We discuss the MathDox system, a system for presenting highly interactive mathematical documents. The system consists of both an XML  format for interactive Mathematical Documents as well as a server for these documents called the MathDox player. }
}

@Article{sTeX,
	author  = {Michael Kohlhase},
	title   = {Using \LaTeX{} as a Semantic Markup Format},
	journal = {Mathematics in Computer Science},
	volume    = {2},
	number    = {2},
	pages     = {279--304},
	year      = {2008},
	url       = {https://doi.org/10.1007/s11786-008-0055-5},
	doi       = {10.1007/s11786-008-0055-5},
	timestamp = {Fri, 26 May 2017 22:54:59 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/journals/mics/Kohlhase08},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@Proceedings{SIGIR:2016,
	editor    = {Raffaele Perego and
		Fabrizio Sebastiani and
		Javed A. Aslam and
		Ian Ruthven and
		Justin Zobel},
	title     = {Proceedings of the 39th International {ACM} {SIGIR} conference on
		Research and Development in Information Retrieval, {SIGIR} 2016, Pisa,
		Italy, July 17-21, 2016},
	publisher = {{ACM}},
	year      = {2016},
	url       = {http://doi.acm.org/10.1145/2911451},
	doi       = {10.1145/2911451},
	isbn      = {978-1-4503-4069-4},
	timestamp = {Thu, 14 Jul 2016 16:07:20 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/sigir/2016},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@Proceedings{CICM:2017,
	editor    = {Herman Geuvers and
		Matthew England and
		Osman Hasan and
		Florian Rabe and
		Olaf Teschke},
	title     = {Intelligent Computer Mathematics - 10th International Conference,
		{CICM} 2017, Edinburgh, UK, July 17-21, 2017, Proceedings},
	series    = {Lecture Notes in Computer Science},
	volume    = {10383},
	publisher = {Springer},
	year      = {2017},
	url       = {https://doi.org/10.1007/978-3-319-62075-6},
	doi       = {10.1007/978-3-319-62075-6},
	isbn      = {978-3-319-62074-9},
	timestamp = {Wed, 28 Jun 2017 13:08:49 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/mkm/2017},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@proceedings{CICM:MKM:2015,
	editor    = {Manfred Kerber and
		Jacques Carette and
		Cezary Kaliszyk and
		Florian Rabe and
		Volker Sorge},
	title     = {Intelligent Computer Mathematics - International Conference, {CICM}
		2015, Washington, DC, USA, July 13-17, 2015, Proceedings},
	series    = {Lecture Notes in Computer Science},
	volume    = {9150},
	publisher = {Springer},
	year      = {2015},
	url       = {https://doi.org/10.1007/978-3-319-20615-8},
	doi       = {10.1007/978-3-319-20615-8},
	isbn      = {978-3-319-20614-1},
	timestamp = {Sun, 04 Jun 2017 10:10:26 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/mkm/2015},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@proceedings{CICM:MKM:14,
	editor    = {Stephen M. Watt and
		James H. Davenport and
		Alan P. Sexton and
		Petr Sojka and
		Josef Urban},
	title     = {Intelligent Computer Mathematics - International Conference, {CICM}
		2014, Coimbra, Portugal, July 7-11, 2014. Proceedings},
	series    = {Lecture Notes in Computer Science},
	volume    = {8543},
	publisher = {Springer},
	year      = {2014},
	url       = {https://doi.org/10.1007/978-3-319-08434-3},
	doi       = {10.1007/978-3-319-08434-3},
	isbn      = {978-3-319-08433-6},
	timestamp = {Wed, 17 May 2017 10:54:57 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/mkm/2014},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@Proceedings{CICM:2014:Workshop,
	editor    = {Matthew England and
		James H. Davenport and
		Andrea Kohlhase and
		Michael Kohlhase and
		Paul Libbrecht and
		Walther Neuper and
		Pedro Quaresma and
		Alan P. Sexton and
		Petr Sojka and
		Josef Urban and
		Stephen M. Watt},
	title     = {Joint Proceedings of the MathUI, OpenMath and ThEdu Workshops and
		Work in Progress track at {CICM} co-located with Conferences on Intelligent
		Computer Mathematics {(CICM} 2014), Coimbra, Portugal, July 7-11,
		2014},
	series    = {{CEUR} Workshop Proceedings},
	volume    = {1186},
	publisher = {CEUR-WS.org},
	year      = {2014},
	url       = {http://ceur-ws.org/Vol-1186},
	urn       = {urn:nbn:de:0074-1186-1},
	timestamp = {Mon, 30 May 2016 16:28:38 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/mkm/2014ws},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@Proceedings{CICM:2012,
	editor    = {Johan Jeuring and
		John A. Campbell and
		Jacques Carette and
		Gabriel Dos Reis and
		Petr Sojka and
		Makarius Wenzel and
		Volker Sorge},
	title     = {Intelligent Computer Mathematics - 11th International Conference,
		{AISC} 2012, 19th Symposium, Calculemus 2012, 5th International Workshop,
		{DML} 2012, 11th International Conference, {MKM} 2012, Systems and
		Projects, Held as Part of {CICM} 2012, Bremen, Germany, July 8-13,
		2012. Proceedings},
	series    = {Lecture Notes in Computer Science},
	volume    = {7362},
	publisher = {Springer},
	year      = {2012},
	url       = {https://doi.org/10.1007/978-3-642-31374-5},
	doi       = {10.1007/978-3-642-31374-5},
	isbn      = {978-3-642-31373-8},
	timestamp = {Fri, 19 May 2017 01:25:05 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/aisc/2012},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@Proceedings{CICM:2009,
	editor    = {Jacques Carette and
		Lucas Dixon and
		Claudio Sacerdoti Coen and
		Stephen M. Watt},
	title     = {Intelligent Computer Mathematics, 16th Symposium, Calculemus 2009,
		8th International Conference, {MKM} 2009, Held as Part of {CICM} 2009,
		Grand Bend, Canada, July 6-12, 2009. Proceedings},
	series    = {Lecture Notes in Computer Science},
	volume    = {5625},
	publisher = {Springer},
	year      = {2009},
	url       = {https://doi.org/10.1007/978-3-642-02614-0},
	doi       = {10.1007/978-3-642-02614-0},
	isbn      = {978-3-642-02613-3},
	timestamp = {Thu, 15 Jun 2017 21:43:52 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/mkm/2009},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@Proceedings{ICCS:2011,
	editor    = {Mitsuhisa Sato and
		Satoshi Matsuoka and
		Peter M. A. Sloot and
		G. Dick van Albada and
		Jack Dongarra},
	title     = {Proceedings of the International Conference on Computational Science,
		{ICCS} 2011, Nanyang Technological University, Singapore, 1-3 June,
		2011},
	series    = {Procedia Computer Science},
	volume    = {4},
	publisher = {Elsevier},
	year      = {2011},
	url       = {http://www.sciencedirect.com/science/journal/18770509/4},
	timestamp = {Mon, 11 May 2015 16:37:28 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/iccS/2011},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@Proceedings{AISC:2010,
	editor    = {Serge Autexier and
		Jacques Calmet and
		David Delahaye and
		Patrick D. F. Ion and
		Laurence Rideau and
		Renaud Rioboo and
		Alan P. Sexton},
	title     = {Intelligent Computer Mathematics, 10th International Conference, {AISC}
		2010, 17th Symposium, Calculemus 2010, and 9th International Conference,
		{MKM} 2010, Paris, France, July 5-10, 2010. Proceedings},
	series    = {Lecture Notes in Computer Science},
	volume    = {6167},
	publisher = {Springer},
	year      = {2010},
	url       = {https://doi.org/10.1007/978-3-642-14128-7},
	doi       = {10.1007/978-3-642-14128-7},
	isbn      = {978-3-642-14127-0},
	timestamp = {Fri, 19 May 2017 01:25:05 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/aisc/2010},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@Proceedings{NTCIR:2016,
	editor    = {Noriko Kando and
		Tetsuya Sakai and
		Mark Sanderson},
	title     = {Proceedings of the 12th {NTCIR} Conference on Evaluation of Information
		Access Technologies, National Center of Sciences, Tokyo, Japan, June
		7-10, 2016},
	publisher = {National Institute of Informatics {(NII)}},
	year      = {2016},
	url       = {http://research.nii.ac.jp/ntcir/workshop/OnlineProceedings12/},
	timestamp = {Tue, 07 Feb 2017 18:13:58 +0100},
	biburl    = {http://dblp.uni-trier.de/rec/bib/conf/ntcir/2016},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}

@phdthesis{MORITZ:Dis,
	author    = {Moritz Schubotz},
	title     = {Augmenting Mathematical Formulae for More Effective Querying {\&}
		Efficient Presentation},
	school    = {Technical University of Berlin, Germany},
	year      = {2017},
	url       = {http://d-nb.info/1135201722},
	isbn      = {978-3-7450-6208-3},
	timestamp = {Tue, 20 Jun 2017 17:23:31 +0200},
	biburl    = {http://dblp.uni-trier.de/rec/bib/phd/dnb/Schubotz17},
	bibsource = {dblp computer science bibliography, http://dblp.org}
}
